### 2023-11-17 main.tex
^^

 By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} by using the explici formula for $|\Psi^{''}\rangle$ we obtain 
\begin{equation}\label{ABS_intermediate}
		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+
	%	\sum_{q_{1},q_{2}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\underbrace{N}_{q_{2}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}\\&+\ldots+\Psi^{''}(N,\ldots,N)\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\prod_{x=1}^{L}\beta_{\tau_{x}}\dt%^{1-\delta_{\tau_{x},N}}

@@

	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain

@@

	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\\

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]
	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left[\delta_{\tau_{x},\sigma_{x}}c_{x}+\delta_{\tau_{x},\sigma_{x}}(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]

@@

=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\left[\delta_{\tau_{x},N}c_{x}+(1-\delta_{\tau_{x},N})(1-c_{x})+\beta_{\tau_{x}}c_{x}(1-\delta_{\tau_{x},N})\right]\nonumber\\

@@

=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}

>>>>

 By considering a fixed $\bm{\tau}\in \Omega^{'}$, and by using \eqref{goodTP-S2} the formula for $|\Psi^{''}\rangle$ we obtain 
\begin{align}\label{ABS_intermediate}
		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]

@@

We rewrite the above equation as
%	c_{x}(\sigma_{x})=\delta_{\sigma_{x},N}
%To simplify notation we will assume that the dependence on $\sigma_{x}$ is understood. Using these $c_{x}$ we obtain

@@

	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
	&\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
	=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{L}\prod_{x=1}^{L}\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\nonumber\\
	&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
	\\=&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]

@@

=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{x},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\

@@

%=&\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
We introduce the summation indices $c_{x}\in \{\delta_{\tau_{x},N},1\}$ for all $x\in \{1,\ldots,L\}$.
and we observe that 
	&\sum_{\sigma_{x}=1}^{N}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]
	=
	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
\end{align} Then, we replace the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$ as 
	\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{x}\right)\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
